Turbulence in compact to giant HII regions

### 2021-12-09 strucfunc_paper.tex
Make a start of reorganization of section 2

\section{\boldmath Sample of \hii{} regions}\label{sec:HIIsample}

@@

Previous investigations using the second-order structure function on the velocity field use, in majority, one HII region and their own methodology.
This has the consequences that only the same authors can compare their results in a direct way and the gap in the interpretation between authors doesn't aid the understanding of the topic.
To deal with this issue we choose 9 objects in the \halpha\ emission line and use the the same methodology in all the regions.
This give us the opportunity to compare for first time the structure function of various objects.
We use previous published observational data to characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
Figure \ref{fig:hii-regions} shows the images of our HII region sample and Table \ref{tab:Reg} shows the the physical properties of interest in each region.

@@

\subsection{Observations}

We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
Their observations were initially published by \citet{Garcia-Diaz:2008a}. 
The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).

>>>>

\section{\boldmath Observations of the \hii{} region sample}
\label{sec:HIIsample}

@@

Previous investigations of the centroid velocity structure function in \hii{} regions
have used a variety of methodologies, which makes it difficult to compare results
between different regions.  \citet{arthur2016turbulence} summarise historical results
for the Orion Nebula in their Table~5.
The most significant differences are seen when different emission line tracers are used,
but even when using the same line, there is some variance between different studies
in the derived values for both the velocity dispersion \(\sigma\pos\) and power-law slope \(m\).
It is therefore worthwhile to employ a uniform approach across a variety of different regions.
To that end, we have selected 9 \hii{} regions,
covering a broad range in size and luminosity,
for which good quality mapping of the \ha{} line exists in the literature
or in data archives.
Figure~\ref{fig:hii-regions} shows optical images of
each region in our sample
and Table~\ref{tab:Reg} lists their most important physical parameters.
The derived centroid \ha{} velocity maps are shown in Figure~\ref{fig:velocity-maps}.
Our sample includes three Milky Way regions
(at approximate distance of \num{0.5} to \SI{2}{kpc}),
two regions in the Magellanic Clouds (\num{50} to \SI{60}{kpc}),
and four regions in more distant galaxies of the Local Group
(\num{500} to \SI{800}{kpc}).
Further details of the observations and the sources themselves
are given in the following two sections.

\subsection{Spectroscopic datasets}

\subsubsection{Longslit echelle spectroscopy}
\label{sec:longsl-echelle-spect}

For the Orion Nebula, we use data obtained with the echelle spectrograph attached to the \SI{4}{m} telescope at Kitt Peak National Observatory (KPNO) initially published in
\citet{Doi:2004a}.
These observations cover a \(\SI{3}{arcmin} \times \SI{5}{arcmin}\) region of the
central (Huygens) part of the Orion Nebula.
The data consist of 96 North--South orientated \SI{300}{arcsec} slits,
uniformly spaced at \SI{2}{arcsec} intervals with a width of \SI{0.8}{arcsec}
with a velocity resolution of \SI{8}{km.s^{-1}}. 
For the centroid velocities, we use the intensity-weighted
mean velocities calculated by \citet{Garcia-Diaz:2008a},
who used additional observations with East--West oriented slits
to refine the inter-slit velocity calibration. 
Unlike in the previous analysis of this dataset by \citet{arthur2016turbulence},
we do not mask out regions affected by known high-velocity outflows.
This decision was made for consistency with the analysis of more distant regions,
where such a masking out is not possible.

\subsubsection{FLAMES multi-fiber spectroscopy}
\label{sec:flames-multi-fiber}

\subsubsection{MUSE integral field spectroscopy}
\label{sec:muse-integral-field}

\subsubsection{TAURUS-II Fabry-Perot spectroscopy}
\label{sec:taurus-ii-fabry}

@@
